Exercise 1 

A.1. Calculate the sum of the given expression with a loop 
```{r}
total <-0
for (a in 5:100){
  sum = a^4+5*a^3
  total = total + sum
}
print(total)

```

A.2. Calculate the sum of the given expression without a loop 
```{r}
a<- 5:100
sum(a^4+5*a^3)
```


B. calculate series Un assuming i = Un-1, and j = Un-2. First, initialized i = U1, j= U2. The statements in the while calculates Un where n starts from 3. 
```{r}
i <- 1 
j <- 2
n <- i + j
while(n <41){
  sum <- i + j 
  i <- j
  j <- sum
  n = n+1
}
 print(sum)

```


C. Calculate cos x, sin x(taylor)
```{r}
library(pracma)
x <- as.numeric(readline(prompt="Enterthe value of x: "))
taylor(sin, x, 45)
taylor(cos, x, 45)
```


D. Create a vector of values of e^x * cos x
```{r}
library(pracma)
vec <- NULL
for (x in seq(3, 6, by=0.1)){
  vec <- append(vec, exp(x)*cos(x))
}
vec
```


E. Count numbers of x divisible by 2 
```{r}
counter <- 0
for (x in 1:300){
  if (x%%2 == 0) {counter = counter +1}
}
counter
```
Exercise 2

Solve the given nearly equations using Gaussian Elimination 
```{r}
library(matlib)
coefficients <- matrix(c(1, 2, 3,
               2, -1, 2,
               3,  3, 1), 3, 3, byrow=TRUE)
results<- c(9, -3, 5)
answer <- gaussianElimination(coefficients, results)
cat("The value of x, y and z is: ", round(answer[,4],digits=2))

```

Exercise 3

Use outer function to create the given matrix 
```{r}
r <- 0:4
c <- 0:4
outer(c, r, "+")
```

Exercise 4

COVID 19 Cases in South Korea
a. Data source details 
- Data Science for COVID-19 (DS4C)
- DS4C: Data Science for COVID-19 in South Korea
- https://www.kaggle.com/kimjihoo/coronavirusdataset

```{r}
library(tidyverse)
covidCases = read.csv("C:\\Users\\Admin\\Desktop\\archive\\Case.csv", header = TRUE)
covidCases
```


b. Explain the Unit & Necessity of each variable
- case_id: the ID of the infection case
- province: Special City / Metropolitan City / Province(-do)
- group: TRUE: group infection / FALSE: not group
- infection_case: the infection case (the name of group or other cases)
- confirmed: the accumulated number of the confirmed
- latitude: the latitude of the group (WGS84)
- longitude: the longitude of the group (WGS84)

c. Find the missing values(rows & columns) and replace them with mean(Tidy Dataset)
```{r}
is.na(covidCases)
## no missing values
```


d. Generate the two new variables(Var1:Mean, Var2: Median from available variable)
```{r}
library(dplyr)
numOfRow <- nrow(covidCases)
covidCases$mean <- rep(NA, numOfRow)
covidCases$median <- rep(NA, numOfRow)
covidCases
```

e. Rename the two existing variables

```{r}
covidCases %>%
rename(
    newMean = mean,
    newMedian = median
    )
covidCases
```

f. Create a plot using following instructions (using 7 layers of Grammar of Graphics)
```{r}
library(ggplot2)
## choose "infection_case" as x and "confirmed" as y
ggplot(covidCases, mapping = aes(x = infection_case, y = confirmed)) + geom_point(size=5, color= "red", alpha = 1/5) + facet_grid(rows = vars(confirmed)) + coord_cartesian() + geom_smooth() + xlab("infection_case") + ylab("comfirmed")

ggtitle("graph")
ggsave(filename = "D:\\Data Science\\covid_19_dataset.png", units = "cm", width = 25, height = 25)
```









































