


1. Generate 2 matrices
```{r}

A <- matrix(sample(1:100, 36), 6, 6) 
B <- matrix(sample(500:600, 36), 6, 6) 
range(A)
range(B)

for(i in 1:nrow(A))
{
  cat("Max of row", i, "of Matrix A is ", max(A[i, ]), "\n")
}

for(i in 1:nrow(B))
{
  cat("Max of row", i, "of Matrix B is ", max(B[i, ]), "\n")
}

cat("Diagnol of Matrix A is ", diag(A))
cat("Diagnol of Matrix B is ", diag(B))

x <- A%*%B





```


2. Create a table using dataframe/tibble with the following categories(a to f)

```{r}
first_name <- c("Sothea", 
                "Leapheng", 
                "Jenny", 
                "Nataly", 
                "Sokheng", 
                "Dalya", 
                "Seavpor", 
                "Kimteng", 
                "Manich", 
                "Lynan")

second_name <- c("Youk", 
                 "Ty", 
                 "Sun", 
                 "Chea", 
                 "Kaing", 
                 "Daro", 
                 "Teng", 
                 "Ley", 
                 "Hann", 
                 "thon")

age <- c(10, 13, 16, 18, 78, 96, 56, 56, 32, 45)
ocupation <- rep(c("Teacher", "Engineer"), 5)
place <- rep(c("Siem Reap", "Phnom Penh"), 5)
random_number <- sample(1:10, 10)



df <- data.frame(First_name = first_name,
                 Second_name = second_name,
                 Age = age,
                 ocupation = ocupation,
                 Place = place,
                 Ramdom_number = random_number)

lastCol <- df$Ramdom_number
sum(lastCol)
mean(lastCol)
length(lastCol)


```

3. Create a .txt file (Minimum : 150 words) with the latest news (In English) in cambodia from the official news agency’s website

Link to the article: https://asiatimes.com/2021/01/cambodia-at-risk-of-being-last-in-line-for-vaccines/

```{r}

article <- read_lines("C:\\Users\\Admin\\Desktop\\cambodia-vaccines.txt")
article <-tibble(article)
word_counts <- text_df %>%
  unnest_tokens(word, text) %>%
  count(word, sort = TRUE)

word_counts

# max(word_counts$n)
  
most_repeated_word <- filter(word_counts, word_counts$n == max(word_counts$n)) 
gsub("for", "KIT", article)

ggplot(word_counts, aes(n, word)) +
  theme(
    axis.title.x = element_text(main = "Number of Words", size = 10, face = "bold", color = "green", hjust = 0.5, margin = margin(20, 0, 0, 0)),
    axis.title.y = element_text(main = "List of words", size = 10, face = "bold", color = "yellow", hjust = 0.5, margin = margin(0, 20, 0, 0)),
    plot.title = element_text(main = "Text Mining Using R", size = 10, face = "bold", color = "blue", hjust = 0.5, margin = margin(0, 0, 25, 0))
  )
  

gsave("D:\\Data Science\\dataMining.png", units = "cm", width = 25, height = 25)




```

4. Find the assigned Dataset from the list below and perform the following
Variables
- Newspaper: describes news agencies
- Daily.Circulation..2013: describes the total number of circulation of each news agency in 2013
- Daily.Circulation..2004: describes the total number of circulation of each news agency in 2004 
- Change.in.Daily.Circulation..2004.2013: describes the change in criculation between 2004 and 2013 

Why I chose Newspaer and Daily.Circulation..2004: because I wanted to illustrate the circulation of the specified news agencies in the year 2004. From that I could compare the data to 2013 and show the change in circulation between this period.

```{r}
library("ggplot2")
library("tidyverse")
library("RCurl")

pulitzer = read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/pulitzer/pulitzer-circulation-data.csv")
pulitzer

# is.na(pulitzer)

names(pulitzer)


ggplot(covidCases, aes(Newspaper, Daily.Circulation..2004)) + 
  facet_grid(Daily.Circulation..2004 ~ Daily.Circulation..2013)
  geom_col(color = "orage", fill = "brown")+
  theme(
    axis.title.x = element_text(main = "Newspaper", size = 10, face = "bold", color = "green", hjust = 0.5, margin = margin(20, 0, 0, 0)),
    axis.title.y = element_text(main = "Daily Circulation 2004", size = 10, face = "bold", color = "yellow", hjust = 0.5, margin = margin(0, 20, 0, 0)),
    plot.title = element_text(main = "Daily News Circulation of News Agencies", size = 10, face = "bold", color = "blue", hjust = 0.5, margin = margin(0, 0, 25, 0))
  )

ggsave("D:\\Data Science\\graph.png", units = "cm", width = 25, height = 25)


```











