---
Title: "Task 2"
By: Sakmonysothea

---
*1. Object x <-1:15*
Construct a 5x3 matrix for the value of x.

```{r}
x <- 1:15
dim(x) <- c(5, 3)
print(x)
```

*2. Write a program to generate the following 4x4 matrix*
```
0 0 0 0
0 0 0 0
0 0 0 0
```
```{r}
m = matrix(rep(0, 16), nrow=4, ncol=4, byrow=TRUE)
print(m)
```
*3. Write a program to generate the following 3x8 matrix using*
The object x<-1:8
```
1 2 3 4 5 6 7 8
8 7 6 5 4 3 2 1
3 3 3 3 3 3 3 3
```
```{r}
m <- rbind(1:8, rev(1:8), rep(3, 8))
print(m)
```

*4. Chose two different(x,y) 4x4 matrix to perform the following arithmetic operations*
a. x + y
b. x - y
c. x*y
d. x%*%y
e. Difference between (c) &(d)
f. Inverse of y
g. z<-x/y
h. Transpose of z
i. Diagonal of transpose matrix
```{r}
x <- matrix(sample(1:15, size=16, replace =TRUE), 4, 4, byrow=TRUE)
y <- matrix(sample(1:15, size=16, replace =TRUE), 4, 4, byrow=TRUE)
print(x + y)
print(x - y)
print(x * y)
print(x %*% y)
print("(c) is a normal arithematic operation, multiplying the matrices element by element while (d) is matrix multiplication.")
print(solve(y))
z <- x / y
print(z)
print(t(z))
print(diag(t(z)))
```

*5. Difference between (i) & (ii)*
```{r}
x <- matrix(x <- 1:9, 3, 3, byrow=TRUE)
print(x)
x <- matrix(x <- 1:9, 3, 3)
print(x)
print("(i) arranges the matrix row-wise while (ii) column-wise.")
```

*6. Which function can we use for inner product and outer product in matrix calculation?*
```{r}
print("%*% is used for inner product and %o% for outer product.")
```

*7. Explain the use of all.equal() function in Matrix with a sample program.*
all.equal(x,y) is a utility to compare R objects x and y testing ``near equality''. If they are different, comparison is still made to some extent, and a report of the differences is returned.
```{r}
m1 <- matrix(1:6, ncol=3)
m2 <- matrix(1:6, ncol=3)
print(all.equal(m1, m2))
print(identical(m1, m2))
print(m1 == m2)
```

*8. Explain the use of dim() function with a sample program.*
```dim()``` Retrieve or set the dimension of an object.
```{r}
m <- 1:9
dim(m) <- c(3,3)
print(m)
```

*9. Use of $ operator, and square brackets [] in List with example program.*
```$  and []``` are used to subset vector inside list.
```{r}
l <- list(numbers = c(3, 5), logical = TRUE, strings = c("a", "b", "c"))
print(l)
print(l[3])
print(l[4])
print(l$numbers)
printsum(l$numbers)
print(sum(l[1]))

```

*10. Explain ifelse() with example.*
It is a shorthand function of the traditional if...else statement.
```{r}
a = c(1, 4, 5, 11.4, -56, -1.3)
ifelse(a %% 2 == 0, "even", "odd")
```

*11. Write a program to get the weight and height from the user to calculate the following cases*
a. If your BMI is less than 18.5, it falls within the underweight range.
b. If your BMI is 18.5 to <25, it falls within the normal.
c. If your BMI is 25.0 to <30, it falls within the overweight range.
d. If your BMI is 30.0 or higher, it falls within the obese range.
```{r}
weight <- readline(prompt = "Enter the weight: ")
weight <- as.integer(weight)
weight
height <- readline(prompt = "Enter the height: ")
height <- as.integer(height)
height
bmi = round(weight / ((height/100)^2), 1)
bmi
ifelse(bmi >= 30.0, "Obesity", 
       ifelse(bmi < 30.0 && bmi >= 25.0, "Overweight", 
              ifelse(bmi < 25.0 && bmi >= 18.5, "Normal", "Underweight")
              )
       )
```

*12. Difference between List and Data frame with an example program.*
```list``` creates a list the same way ```c``` creates a vector. However, lists do not group together individual values; lists group together R objects, such as atomic vectors and other lists.
Data frames are the two-dimensional version of a list. It is the most useful storage structure for data analysis. It stores data in an excel spreadsheet format.
```{r}
l1 <- list(35: 53, "R", list(TRUE, FALSE))
l1
```
```{r}
d <- data.frame(app = c("apple", "pineapple", "pen"),
                 car = c("bmw", "ferrari", "audi"), value = c(1, 2, 3))
d
```

*13. Difference between repeat and while loop with example program*
They are companions to the ```for``` loop. ```while``` loop will take condition to run the loop whereas ```repeat``` doesn't take condition but we need to call ```break``` to exit the loop.
```{r}
j <- 5
while (j>=0){
  j <- j-1
  print("Hello world")
}

i <- c(2,5,3,9,8,11,6)
count <- 0
for (val in i) {
if(val %% 2 == 0)  count = count+1
}
print(count)


```

